---
title: "Marcin Cencek"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: ["linkedin"]
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(openintro)
library(highcharter)


```

```{r}
data <- read.csv("~/Desktop/R/BeerProject/data.csv")
```


```{r}


```

```{r}
mycolors <- c("blue","#FFC125","darkgreen","darkorange")
```

Home
==================

Row
------------------

### Average Arrival Delays in Minutes

```{r}
valueBox(paste('Data July 2021'),
color = 'olivedrab')
```



### Overall Average Score

```{r}
gauge(round(mean(data$rating_score),
            digits = 2),
            min = 0,
            max = 5,
            gaugeSectors(success = c(0,2),
                         warning = c(2,4),
                         danger = c(4,5),
                         colors = c('red','yellow','green')))
```


### Total Number of Points
```{r}
valueBox(length(data$beer_name),
         icon = 'glyphicon glyphicon-plane')
```

Column {data-width=350}
-----------------------------------------------------------------------

### Top States Based on Count of Flights of Origin

```{r}

          
```


### Top 10 Airports Based on Count of Flights of Origin


```{r}

          
```

Row
---------------------

### Distance vs Air Time

```{r}

```

### Day of Month vs Count of Flights

```{r}

                   


```

Map
=========================


```{r}


```


Delays by Airport
=========================
```{r}


```

Departure Time Blocks
=========================

```{r}

```

Carriers Distance and Delays
=========================

Row
-------------------------
### Carriers and Distance

```{r}

```
Row
-------------------------

### Carrier Arrival Delay Distribution

```{r}

```

Summary {data-orientation=columns}
=========================

Column {data-width = 100}
-------------------------

### Longest Delay in Minutes
```{r}

```

### Average Arrival Delay in Minutes
```{r}

```

### Average Flight Distance in Miles
```{r}

```

### Standard Deviation of Arrival Delays
```{r}

```

### Maximum Flight Distance in Miles
```{r}

```

### Standard Deviation of Distance
```{r}

```



About Report
=========================

<b><font face="arial" size="4" color="#000000">Created by Marcin W. Cencek</font></b>

<a href="mailto:marcin.cencek@gmail.com">marcin.cencek@gmail.com</a>

* Fun Project




